Comparing OTU quality across clustering strategies

### 2021-05-10 exploratory/2021/compare-strategies_2021-05.Rmd
auto figure size

@@

# with facet_grid()

@@

## with cowplot

```{r otu-quality_cowplot, fig.width=4, fig.height=2}
plot_quality <- function(dat, y_val, title = '') {
  dat %>% 
    ggplot(aes(strategy, {{ y_val }}, color = method)) + 
    geom_hline(data = sum_opticlust, aes(yintercept = {{ y_val }})) +
    geom_point() +
    facet_wrap(dataset ~ ., nrow=1) +
    scale_color_manual(values = tri_colors) +
    ylim(0, 1) +
    coord_flip() +
    labs(x = '', y = '', title = title) + 
    theme(legend.position="none")
}
mcc_plot <- sum_optifit %>% 
  plot_quality(mcc_median, title = 'Median MCC')
frac_plot <- sum_optifit %>% 
  plot_quality(frac_map_median, title = 'Median fraction mapped')  + 
  labs(caption = "Black line: _de novo_ clustering") +
  theme(plot.caption = element_markdown(hjust = 0),
        plot.caption.position = 'plot')

>>>>

### data prep

@@

# using facet_grid()

@@

## using cowplot

```{r otu-quality_cowplot}
plot_quality <- function(dat, y_val, title = '') {
  dat %>% 
    ggplot(aes(strategy, {{ y_val }}, color = method)) + 
    geom_hline(data = sum_opticlust, aes(yintercept = {{ y_val }})) +
    geom_point() +
    facet_wrap(dataset ~ ., nrow=1) +
    scale_color_manual(values = tri_colors) +
    ylim(0, 1) +
    coord_flip() +
    labs(x = '', y = '', title = title) + 
    theme(legend.position="none")
}
mcc_plot <- sum_optifit %>% 
  plot_quality(mcc_median, title = 'Median MCC')
frac_plot <- sum_optifit %>% 
  plot_quality(frac_map_median, title = 'Median fraction mapped')  + 
  labs(caption = "Black line: _de novo_ clustering") +
  theme(plot.caption = element_markdown(hjust = 0),
        plot.caption.position = 'plot')
